%-----------PROJECTS-----------%
\section{Projects}
  \resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{Toldio E-commerce Platform (Freelance Project)} $|$ \emph{Next.js, Node.js}}
  {\href{https://market.tolido-group.com/}{\textit{Live}}}
\resumeItemListStart
  \resumeItem{Built a full e-commerce platform with multi-region and bilingual (AR/EN) support.}
  \resumeItem{Developed frontend (Next.js, React, Tailwind, AntD) and backend (Node.js, MongoDB).}
  \resumeItem{Implemented CRM with role-based access, optimized product queries, advanced search, and a CME for dynamic content control.}
  \resumeItem{Integrated Cloudinary, gtag, and deployed on a Hostinger VPS using Docker.}
\resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Ktabook Smart eBook Platform} $|$ \emph{.NET, React, Flask}}
      {\href{https://drive.google.com/drive/u/0/folders/1DsX92rg3zdS49gtNKVVEww_Jaei0H10l}{\textit{Demo}}}
      \resumeItemListStart
        \resumeItem{Developed a digital library platform for reading, listening, and community engagement.}
        \resumeItem{Implemented AI-driven text-to-speech, personalized book recommendations, and automated content moderation.}
        \resumeItem{Managed a 12,000-book dataset, multilingual support, and admin dashboards.}
        \resumeItem{Built with React for the frontend, Flask and .NET for the backend, and SignalR for real-time interactions, ensuring an inclusive experience for global users.}
      \resumeItemListEnd


 \resumeProjectHeading
  {\textbf{Dash-Stack Admin Dashboard} $|$ \emph{Next.js, Supabase}}
  {\href{https://drive.google.com/drive/u/0/folders/1WN3Acgj82jD1tdp-6DKfsWKgoLXlWSr2}{\textit{Demo}}}
\resumeItemListStart
  \resumeItem{Built an admin dashboard with data visualization, file management (uploads, QR codes), and full CRUD features.}
  \resumeItem{Designed for admins/users to manage and view shared digital content such as menus.}
\resumeItemListEnd



  \resumeSubHeadingListEnd
